---
title       : Miles per Gallon Prediction App
subtitle    : Data Products Course Presentation
author      : Michael Bausor
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : yesterday      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## The Problem

Are you:

- Buying a new car?
- Selling a car?
- Trying to save money on fuel?

You need to know the mileage you can expect to get out of your car. But how? Trying to calculate the mileage of a car yourself, you can encounter all sorts of problems, such as:

- Tricky and error prone measurements
- Boring maths
- Mind numbing apathy

Is there another way?

--- .class #id 

## The Solution

YES! 

Our state of the art prediction app can tell you the miles per gallon of your car with just the click of a button.

Simply enter the weight and transmission type of you car, and BOOM! Out comes the miles per gallon. It really is that easy!

```{r fk, eval=FALSE, echo=TRUE}
weight + transmission = mpg prediction
mpg prediction + you = profit
```

--- .class #id 

## Prediction...with SCIENCE

Our state of the art prediction algorithm utilizes strong correlation between car weight and miles per gallon performance, as shown in the following chart.

```{r fit, fig.width=12, fig.height=6, echo=FALSE}
library(ggplot2)
library(plyr)
library(gridExtra)
mtcars$Transmission<-revalue(factor(mtcars$am),c("0"="Auto", "1"="Manual"))
mtauto<-mtcars[mtcars$am==0,]
mtman<-mtcars[mtcars$am==1,]
fit<-lm(mtcars$mpg ~ mtcars$wt)
fitauto <- lm(mtauto$mpg ~ mtauto$wt)
fitman <- lm(mtman$mpg ~ mtman$wt)
b0<- fit$coefficients[1]
b1<- fit$coefficients[2]
b0a<- fitauto$coefficients[1]
b1a<- fitauto$coefficients[2]
b0m<- fitman$coefficients[1]
b1m<- fitman$coefficients[2]
ggplot(mtcars, aes(x=wt, y=mpg, colour=Transmission)) + 
    geom_point() + 
    geom_line(aes(y=wt*b1+b0, colour="Regression")) +
    geom_line(aes(y=wt*b1a+b0a, colour="Regression Auto")) +
    geom_line(aes(y=wt*b1m+b0m, colour="Regression Manual")) +
    xlab("Weight (lb/1000)") +
    ylab("Miles per gallon (mpg)")
```

--- .class #id 

## Do it NOW

You can find out the miles per gallon of your car right now! Just follow these simple steps:

1. Go to https://michaelbausor.shinyapps.io/Project
2. Enter your car's weight and transmission type
3. Press submit
4. Victory!
